---
title: "data analysis exercise"
output:
  html_document:
    toc: FALSE
---

#data description This data set was found on [data.cdc.gov](https://data.cdc.gov/Foodborne-Waterborne-and-Related-Diseases/Botulism/66i6-hisz). The data set contains the information regarding the reported botulism cases, a national notifiable disease, reported in the United states. There are five variables presented in the header: State, Year, BotType (the type of transmission), ToxinType (the type of toxin), and Count (reported cases)

#Setup load packages



```{r}
library(readr)#for loading csv file
library(here)#to set relative paths
library(dplyr)#for data processing and cleaning
library(tidyr)#for data processing and cleaning
library(skimr)#for browsing data
library(forcats)#for processing categorical data
library(lubridate)#for processing date/time
library(ggplot2)
```

#data loading

```{r}
data_location=here("exercise","data","raw_data","Botulism.csv")
botulism=read_csv(data_location)
```

#checking data

```{r}
#checking the variable type
glimpse(botulism)
#checking the first few row of raw data
head(botulism,n=10)
```

#data cleaning after checking the data, R consider the numbers under `Year` as regular numbers (double), so we need to change it to character; Also, I consider `Count` as the outcome of interest, `ToxinType` & `BotType` might associate with the outcome in certain way. I am also interested in the spread of botulism-infection cases in the `states` and in different `years`.

```{r}
#convert Year to character
d1=botulism%>%
 mutate(Year=as.character(Year))
#check
skim(d1)
glimpse(d1)
#convert Toxin type to a categorical variable
d2=d1%>%
  mutate(ToxinType=as_factor(ToxinType),BotType=as_factor(BotType))
#check d2
skim(d2)
glimpse(d2)
summary(d2)
```

#save data

```{r}
#assign the processed data to an object called processeddata
processeddata=d2
#set a relative path for saved data
save_data_location=here("exercise","data","processed_data","processeddata.rds")
saveRDS(processeddata,file=save_data_location)
```

## Deanna Lanier Additions

```{r}
# read .rds file
data_location=here("exercise","data","processed_data","processeddata.rds")
processedData = readRDS(data_location)

```

```{r}
#Get Summary
summary(processedData)
```

Determine specific years to visualize

```{r}
processedData = processedData %>% 
  mutate_at(
    vars('Year'), 
    as_date,
    format = "%y"
    )

processedData%>%
  count(Year)
```

Focus on years 2000-2017

```{r}
processedData = processedData %>% filter(Year >='2000-01-01' ) 

processedData%>%
  count(Year)
```

**What are the types of botulism found in this dataset?**

```{r}
processedData %>% pull(BotType) %>% unique()
```

**What type of botulism was the most prevalent from 2000-2017**

```{r}
#Create table of the sums of the count column based on conditions 
botulism_2000s =  data.frame (BotType  = c("Foodborn", "Infant", "Wound", "other"),
                  Total = c(sum(processedData[which(processedData$BotType=='Foodborne'), 5]), sum(processedData[which(processedData$BotType=='Infant'), 5]),sum(processedData[which(processedData$BotType=='Wound'), 5]),sum(processedData[which(processedData$BotType=='Other'), 5]))
                  )
botulism_2000s
```

Infant is the most prevalent type of botulism from 2000-2017. Followed by wound and foodborne.

**What is the prevalence of the types each year?**

```{r}
#Plot Botulism types
botulism_plot = ggplot(processedData, aes(fill=BotType, y=Count, x=Year)) + 
    geom_bar(position="dodge", stat="identity")+scale_x_date(date_breaks = "1 year", date_labels = "%Y")+theme(legend.position = "bottom",axis.text.x = element_text(size = 10, angle=60, hjust=1))+ggtitle("Types of Botulism Cases between 2000 and 2017")+theme(plot.title = element_text(hjust = 0.5))

botulism_plot
```

**What toxins are leading in infant botulism?**

```{r}
Infant = processedData %>% filter(BotType == "Infant", Year >='2000-01-01' )

#Plot Foodborn Botulism 
infant_plot = ggplot(Infant, aes(fill=ToxinType, y=Count, x=Year)) + 
    geom_bar(position="dodge", stat="identity")+scale_x_date(date_breaks = "1 year", date_labels = "%Y")+theme(legend.position = "bottom",axis.text.x = element_text(size = 10, angle=60, hjust=1))+ggtitle("Infant Botulism types for 2000-2017")+theme(plot.title = element_text(hjust = 0.5))

infant_plot
```

The most prominent toxin type in infant botulism between 2000 and 2017 is toxin A
