---
title: "EDA"
author: "Weifan Wu"
editor: visual
output:html_document
date:"02/25/2023"
---

##EDA
#Main continous outcome of interest is `Body Temperature`, and main categorical outcome is `Nausea` #Load Library install.packages("DataExplorer")

```{r}
library(tidyverse)
library(here)
library(skimr)
library(tidymodels)
library(gtsummary)
library(ggstatsplot)
library(DataExplorer)
```

#Load Data

```{r}
data_location=here("fluanalysis","data","processeddata.rds")
exp_data=readRDS("processeddata.rds",file=data_location)
```

#Check Data

```{r}
skim(exp_data)
```

#Get Summary Tables

```{r}
#Get Summary Table for exp_data, grouped by Nausea
tbl_summary(exp_data,by=Nausea)
```

#Histogram and Density plot for for Body Temperature

```{r}
plot_histogram(exp_data)
plot_density(exp_data)
```

#It appears that the Body Temperature is right skewed, which is expected. However, let's check for outliers

#The predictors that I choose include: Vomitting, Diarrhea, Weakness, Insomnia, and RunnyNose

```{r}
#Headache VS 
#Nausea VS a Diarrhea
ggbarstats(data=exp_data,x=Nausea,y=Diarrhea,label="both")
```
