---
title: "EDA"
author: "Weifan Wu"
editor: visual
output:html_document
date:"02/25/2023"
---

##EDA
#Main continous outcome of interest is `Body Temperature`, and main categorical outcome is `Nausea` #Load Library 
```{r}
library(tidyverse)
library(here)
library(skimr)
library(gtsummary)
library(ggstatsplot)
library(ggbeeswarm)
library(DataExplorer)
```

#Load Data

```{r}
data_location2=here("fluanalysis","data","processed_data.rds")
exp_data=readRDS("processed_data.rds", file=data_location2)
```

#Check Data

```{r}
head(exp_data)
skim(exp_data)
view(exp_data)
```

#Get Summary Tables

```{r}
#Get Summary Table for exp_data, grouped by Nausea
tbl_summary(exp_data,by=Nausea)
```

#Histogram and Density plot for for Body Temperature

```{r}
plot_histogram(exp_data)
plot_density(exp_data)
```

#It appears that the Body Temperature is right skewed, which is expected. Data distributed within a reasonable range (~97-103).let's check for normality
```{r}
plot_qq(exp_data)
```

##Exploration of the relationships between outcomes and predictors
#The predictors that I choose include:  ChillsSweats, Vomit, Weakness, ChestPain, and RunnyNose
#the outcomes are BodyTemp and Nausea

```{r}
# Explore all predictor variables vs `BodyTemp` 

# `ChillsSweats` VS `BodyTemp` 
ggplot(exp_data,aes(x=ChillsSweats, y=BodyTemp))+
  geom_boxplot()
# It appears that the median temperature is slightly higher in the population who have chillsweats VS no chillsweats. There are more samples that have high body temperature (>102 degree) in the group with chillssweats symptom.

#`Vomit` VS `BodyTemp` grouped by weakness
ggplot(exp_data,aes(x=Vomit, y=BodyTemp,color=Weakness))+
  geom_quasirandom(alpha=0.5,varwidth=TRUE)+
  stat_summary(fun=median,geom="crossbar")
#There are more people who have no vomit than people who suffer vomit. Most people have moderate weakness.

# `Weakness` levels VS `BodyTemp`
ggplot(exp_data,aes(x=Weakness, y=BodyTemp))+
  geom_boxplot()
#It seems like overall the severe weakness comes with highest median temperature, which is expected

# `ChestPain` VS `BodyTemp`
ggplot(exp_data,aes(x=ChestPain, y=BodyTemp))+
  geom_quasirandom(alpha=0.5,varwidth=TRUE)+
  stat_summary(fun=median,geom="crossbar")

# `RunnyNose` vs `BodyTemp`group by weakness levels
ggplot(exp_data,aes(x=RunnyNose, y=BodyTemp))+
 geom_quasirandom(alpha=0.5,varwidth=TRUE)+
  stat_summary(fun=median,geom="crossbar")

#`Vomit` VS `BodyTemp`
ggplot(exp_data,aes(x=Vomit, y=BodyTemp))+
geom_quasirandom(alpha=0.5,varwidth=TRUE)+
  stat_summary(fun=median,geom="crossbar")
```
ChillsSweats, Vomit, Weakness, ChestPain, and RunnyNose

```{r}
#Let's check if there's any pattern between outcome `Nausea` VS all the predictor variables
# `Nausea` VS `ChillsSweats`
ggbarstats(data=exp_data,x=Nausea,y=ChillsSweats,label="both")
# `Nausea` VS `Vomit`
ggbarstats(data=exp_data,x=Nausea,y=Vomit,label="both")
# `Nausea` VS `Weakness`
ggbarstats(data=exp_data,x=Nausea,y= Weakness,label="both")
# `Nausea` VS `ChestPain`
ggbarstats(data=exp_data,x=Nausea,y=ChestPain,label="both")
# `Nausea` VS `RunnyNose`
ggbarstats(data=exp_data,x=Nausea,y=RunnyNose,label="both")
```
#It seems like other than RunnyNose, every other predictors have a clear relationship with Nausea



